\documentclass[../main.tex]{subfiles}
\begin{document}

\resumeSubHeadingListStart

    \resumeProjectHeading
        {
            \titleItem{E-Commerce Platform with Microservices}\pipe
            \emph{NestJS, GraphQL, MongoDB, Redis, Kubernetes}
        }
        {2023}
    \resumeItemListStart
        \resumeItem{Engineered a microservices-based e-commerce platform with NestJS, GraphQL APIs, and MongoDB for product and order management.}
        \resumeItem{Used Redis for caching and Kubernetes for orchestration and scaling.}
    \resumeItemListEnd

    \resumeProjectHeading
        {
            \titleItem{Progressive Web App for Task Management}\pipe
            \emph{Vue.js, PWA, Service Workers, GCP}
        }
        {2023}
    \resumeItemListStart
        \resumeItem{Created a mobile-first PWA for task management with offline support using Vue.js and Service Workers.}
        \resumeItem{Deployed on Google Cloud Platform with automated CI/CD.}
    \resumeItemListEnd

    \resumeProjectHeading
        {
            \titleItem{Serverless Event-Driven System}\pipe
            \emph{AWS Lambda, DynamoDB, S3, API Gateway}
        }
        {2022}
    \resumeItemListStart
        \resumeItem{Designed a serverless backend for event processing and notifications using AWS Lambda, DynamoDB, and S3.}
        \resumeItem{Exposed RESTful endpoints via API Gateway and implemented monitoring with CloudWatch.}
    \resumeItemListEnd

    \resumeProjectHeading
        {
            \titleItem{Secure Authentication \& Authorization System}\pipe
            \emph{OAuth2, JWT, Auth0, Express}
        }
        {2022}
    \resumeItemListStart
        \resumeItem{Implemented a robust authentication and authorization system using OAuth2, JWT, and Auth0 for a multi-user web application.}
        \resumeItem{Integrated with Express.js middleware for secure API access and session management.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}